Crop adaptation through gene flow

### 2016-06-29 crop_adaptation_gene_flow_gj_outline.tex
Update crop_adaptation_gene_flow_gj_outline.tex

Morphological similarities indicate that wild, weedy, and cultivated olives form an interfertile species complex that sprawls across the Mediterranean, and that outbreeding with these wild and weedy relatives has contributed to olive's genetic diversity, but it has not been shown that locally-adapted genes have been introgressed into the domesticated olive \cite{zohary1975beginnings}\.

>>>>

Olives (Olea europaea subsp. europaea var. sativa) were domesticated primarily in the northeastern Levant and then dispersed west along the length of the Mediterranean range of wild (var. oleaster) olives \cite{besnard2013complex}\.
The prevalence of wild olives (var. oleaster) has since been diminished.

Morphological similarities indicate that wild, weedy, and cultivated olives form an interfertile species complex that sprawls across the Mediterranean, and that outbreeding with these wild and weedy relatives has contributed to cultivated olive's genetic diversity, but it has not been specifically shown that locally-adapted genes have been introgressed into the domesticated olive \cite{zohary1975beginnings}\.

Olives have been propogated clonally for much of their history, limiting gene flow, but given the chance, cultivated and wild olives are fully interfertile [[green and wickens 1989]].
Feral cultivated/wild hybrid oleasters are evidence of such outcrossing events.
